Binary companions of red giant stars in \apogee\ \DR

### 2018-02-25 paper/1-catalog/twoface-catalog.tex
title tweak; abstract work

\title{Binary companions of red giant stars with APOGEE DR14}

@@

\begin{abstract}\noindent % trust me
% Context
Repeat radial-velocity measurements of stars can be used to identify stellar,
sub-stellar, and planetary-mass companions.
Even sparse or few-epoch observations are useful for detecting companions,
though such data are difficult to use for measuring physical properties of
individual systems because permitted orbital solutions can be highly degenerate.
% Aims
Using a custom-built Monte Carlo sampler (\thejoker) to deliver (often highly
multi-modal) posterior beliefs about companion orbital parameters, here we
perform a search for secondary companions of over 100,000 stars observed by the
\apogee\ survey (\DR) with $\geq 3$ epochs.
% Methods
We select stars with probable companions by \todo{how?}.
% Results
We provide (1) a catalog of \ncompanions\ companions for which the companion
properties can be confidently determined, (2) a catalog of stars that likely
have companions, but for  which more observations are needed to uniquely
determine the orbital properties, and (3) posterior samplings for all \nstars\
stars in the parent sample.
We highlight interesting systems and show the characteristics of stars with
confidently determined companion properties.
\end{abstract}

>>>>

\title{Binary companions of red giant stars in \apogee\ \DR}

@@

\begin{abstract}\noindent % trust me
% Context
Repeat radial-velocity measurements of stars can be used to identify stellar,
sub-stellar, and planetary-mass companions.
Even a very small number of observation epochs can be useful for detecting companions,
though such data can be difficult to use for characterizing
individual systems:
There can be multiple qualitatively different orbital solutions that fit the data.
For these reasons, we custom-built a Monte Carlo sampler (\thejoker)
that delivers reliable (and often highly
multi-modal) posterior samplings for companion orbital parameters given sparse
radial-velocity data.
% Aims
Here we
perform a search for secondary companions of over 100,000 red-giant
stars observed in the
\apogee\ survey (\DR) with $\geq 3$ spectroscopic epochs.
% Methods
We select stars with probable companions by making a cut on our posterior belief about
the amplitude of the stellar radial-velocity variation induced by the orbit \todo{do we?}.
% Results
We provide (1)~a catalog of \ncompanions\ companions for which the stellar companion
properties can be confidently determined in a posterior sense,
(2)~a catalog of stars that likely
have companions, but for which (in most cases) more observations
would be needed to uniquely
determine the orbital properties, and (3)~posterior samplings for all orbital-companion
parameters for all \nstars\
stars in the parent sample.
We highlight interesting systems and show the characteristics of stars with
confidently determined companion properties.
\end{abstract}
